Introduction to Structural Causal Models

### 2021-05-28 scm_short_presentation.Rmd
cxyt

- Noise terms independent 
- Mechanisms independent/autonomous 
- Set of equations 
- Endogenous and Exogenous Variables

@@

>>>>

- Mechanisms independent/autonomous 
- Set of equations (assignments ':=')
- Observational Data 
- Endogenous and Exogenous Variables
- Latent noise variables 
- Noise terms independent

@@

Do you have any concepts that are still unclear to you?
